Millions of Type Errors

### 2023-05-03 oopsla23/paper.tex
Update paper.tex
Added email addresses
table, by-mode add/remove error
quick module switch numbers

\usepackage{alltt}
% \usepackage{amssymb} -- already loaded by acmart
\usepackage{calc}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{tikz}
\usepackage{wasysym}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\author{Alan Jeffrey}
\orcid{0000-0001-6342-0318}
\affiliation{%
  \institution{Roblox}
  \city{San Mateo}
  \state{California}
  \country{USA}
}
\email{}

@@

\author{Mitesh Shah}
\orcid{TODO}
\affiliation{%
  \institution{Roblox}
  \city{San Mateo}
  \state{California}
  \country{USA}
}
\email{}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}

@@

  Errors in edit region.
  Each record with an edit region error adds +1 to at least 1 row.

@@

@@

>>>>

\usepackage{alltt}
% \usepackage{amssymb} -- already loaded by acmart
\usepackage{calc}
\usepackage{cleveref}
\usepackage{listings}
\usepackage{mathpartir}
\usepackage{pifont}
\usepackage{siunitx}
\usepackage{tikz}
\usepackage{wasysym}
\usepackage{wrapfig}
\usepackage{xcolor}
\usetikzlibrary{shapes.geometric}

@@

\author{Alan Jeffrey}
\orcid{0000-0001-6342-0318}
\affiliation{%
  \institution{Roblox}
  \city{San Mateo}
  \state{California}
  \country{USA}
}
\email{ajeffrey@roblox.com}

@@

\author{Mitesh Shah}
\orcid{TODO}
\affiliation{%
  \institution{Roblox}
  \city{San Mateo}
  \state{California}
  \country{USA}
}
\email{mshah@roblox.com}

@@

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FILL}{\textbf{FILL}}
\newcommand{\dotscale}[1]{\scalebox{0.72}{#1}}
\newcommand{\wideas}[2]{\makebox[\widthof{#2}][l]{#1}}
\newcommand{\twoline}[2]{\parbox[s]{1.4cm}{\flushleft#1\newline#2}}
\newcommand{\chkYes}{\dotscale{\CIRCLE}}
\newcommand{\chkMaybe}{\wideas{\dotscale{\Circle}}{\chkYes}}
\newcommand{\chkNo}{\wideas{}{\chkYes}}
\newcommand{\pct}[1]{\SI{#1}{\percent}}

@@

  Below, edit region only.
  Each record with an edit region error adds +1 to at least 1 row.

  \smallskip

@@

\begin{figure}[t]

  {Few local adds => Few people ignoring script analysis}
  \smallskip

  \begin{tabular}{lrrrr}
    & Local Remove & Local Add & Nonlocal Remove & Nonlocal Add \\
    Mode
    & \#err (count)
    & \#err (count)
    & \#err (count)
    & \#err (count) \\\midrule
    \code{nocheck}   & 86 (71) & 0 (0) & 110 (57) & 161 (74) \\
    \code{nonstrict} & 87 (25) & 9 (3) & 185 (29) & 207 (37) \\
    \code{strict}    &  1  (1) & 0 (0) &  14  (6) &   6  (3) \\
  \end{tabular}

  \caption{Per-mode comparison}
  \label{f:mode-errors}
\end{figure}

@@

\subsection{Module Switches}

FILL need \%s out of all module switches.

How many module switches exit a module with errors?
nocheck 24, nonstrict 9, strict 3.
Rare?
More common for forcedstrict:
 nocheck 190, nonstrict 16, strict 2.

How many module switches go to a module with errors?
nocheck 70, nonstrict 9, strict 4
For FS: nocheck 400, nonstrict 39, strict 6.
